Visualizations for the manuscript

### 2022-05-13 metanalysis_visualization/manuscript_Figures.Rmd
pvalues prsentation with a table

```{r}
pvalues_boot_before <- bootstrapped_coefficients_all %>% 
  left_join(filter(coefficients_df, term == "time"), by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "before_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid")

pvalues_boot_after <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df %>%
              pivot_wider(names_from = term,
                          values_from = observed_slope_coefficient) %>% 
              mutate(observed_slope_coefficient = time + `periodduring_pandemic:time`) %>% 
              select(siteid, observed_slope_coefficient),
            by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "during_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid")

>>>>

```{r}
pvalues_boot_before <- bootstrapped_coefficients_all %>% 
  left_join(filter(coefficients_df, term == "time"), by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "before_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid") %>% 
  mutate(string = paste0(observed_slope_coefficient, " (", pvalue, ")")) %>% 
  mutate(string = paste0(observed_slope_coefficient, " (", format.pval(pvalue,
                                                                       digits = 2,
                                                                       eps = 10**-3, 
                                                                       nsmall = 2),
                         ")")) %>% 
  select(siteid, string) %>% 
  rename("Before pandemic trend (p-value)" = string)

pvalues_boot_after <- bootstrapped_coefficients_all %>% 
  left_join(coefficients_df %>%
              pivot_wider(names_from = term,
                          values_from = observed_slope_coefficient) %>% 
              mutate(observed_slope_coefficient = time + `periodduring_pandemic:time`) %>% 
              select(siteid, observed_slope_coefficient),
            by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "during_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid")%>% 
  mutate(string = paste0(observed_slope_coefficient, " (", format.pval(pvalue,
                                                                       digits = 2,
                                                                       eps = 10**-3, 
                                                                       nsmall = 2),
                         ")")) %>% 
  select(siteid, string) %>% 
  rename("Since pandemic trend (p-value)" = string)

pvalues_boot_difference <- bootstrapped_coefficients_all %>% 
  left_join(filter(coefficients_df, term == "periodduring_pandemic:time"), by = "siteid") %>% 
  group_by(siteid) %>% 
  group_map( bootstrap_pvalue_calculation, slope_name = "difference_slope" ) %>% 
  setNames(unique(bootstrapped_coefficients_all$siteid)) %>% 
  bind_rows(.id = "siteid") %>% 
  mutate(string = paste0(observed_slope_coefficient, " (", pvalue, ")")) %>% 
  mutate(string = paste0(observed_slope_coefficient, " (", format.pval(pvalue,
                                                                       digits = 2,
                                                                       eps = 10**-3, 
                                                                       nsmall = 2),
                         ")")) %>% 
  select(siteid, string) %>% 
  rename("Before/since pandemic trend difference (p-value)" = string)

inner_join(pvalues_boot_before, pvalues_boot_after) %>% 
  inner_join(pvalues_boot_difference) %>% 
  inner_join(country_map) %>% 
  select(plotsLabel, everything(), -country, -siteid) %>% 
  arrange(plotsLabel) 
# %>% 
#   flextable::flextable() %>% 
#   flextable::autofit() %>% 
#   flextable::save_as_docx(path = "trends_pval.docx")
